\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{booktabs}

% Colors
\definecolor{newitem}{RGB}{0,100,0}

% Header/Footer
\pagestyle{fancy}
\fancyhf{}
\rhead{CS 4300/5300 Software Engineering}
\lhead{Sprint 4}
\rfoot{Page \thepage}

% Section formatting
\titleformat{\section}{\Large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries}{\thesubsection}{1em}{}

\begin{document}

\begin{center}
{\LARGE\textbf{CS 4300/5300 Software Engineering}}\\[0.5em]
{\Large Sprint 4 Requirements}\\[1em]
\end{center}

\section{Sprint 4 Objectives}

\begin{center}
\begin{tabular}{lc}
\toprule
\textbf{Requirement} & \textbf{Points} \\
\midrule
Individually - Delivered Peer Feedback & 12 pts \\
Project in GitHub & 0 pts \\
Features with tests & 10 pts \\
80\% Test coverage metrics & 15 pts \\
\midrule
\multicolumn{2}{l}{\textbf{CI Pipeline:}} \\
\quad AI Code Review using OpenAI Platform (each Pull Request) & 2.5 pts \\
\quad Running automated tests (each commit) & 1.5 pts \\
\quad Reports test coverage metrics in console (each commit) & 1.5 pts \\
\quad PyLint and/or Flake8: Linting scans w/ reports & 5 pts \\
\quad Dependabot: Dependency Vulnerability Scans w/ reports & 5 pts \\
\midrule
\multicolumn{2}{l}{\textbf{Deployed to a production environment:}} \\
\quad Custom domain name (no subdomains unless you own TLD) & 5 pts \\
\midrule
CD Pipeline that runs when code is merged into main & 2.5 pts \\
\midrule
\textcolor{newitem}{\textbf{NEW:}} 100\% of vulnerabilities and linter findings addressed/fixed & 20 pts \\
\textcolor{newitem}{\textbf{NEW:}} 5 Minute Marketing Video uploaded to YouTube & 20 pts \\
\midrule
\textbf{Total} & \textbf{100 pts} \\
\bottomrule
\end{tabular}
\end{center}

\section{Detailed Requirements}

\subsection{Individually - Delivered Peer Feedback (12 pts)}
Each team member must deliver constructive peer feedback to teammates.

\subsection{Project in GitHub (0 pts)}
Your project must continue to be maintained in GitHub (no points assigned as this is now expected).

\subsection{Features with Tests (10 pts)}
All features developed during this sprint must have corresponding tests.

\subsection{80\% Test Coverage Metrics (15 pts)}
Your test suite must maintain at least 80\% code coverage.

\subsection{CI Pipeline (15.5 pts total)}
Your continuous integration pipeline must include:
\begin{itemize}
    \item \textbf{AI Code Review (2.5 pts):} Using OpenAI Platform for each Pull Request
    \item \textbf{Automated Tests (1.5 pts):} Running automated tests for each commit
    \item \textbf{Coverage Reports (1.5 pts):} Reports test coverage metrics in console for each commit
    \item \textbf{Linting (5 pts):} PyLint and/or Flake8 linting scans in CI pipeline with reports
    \item \textbf{Dependency Scans (5 pts):} Dependabot dependency vulnerability scans in CI pipeline with reports
\end{itemize}

\subsection{Custom Domain (5 pts)}
Your application must be deployed to a production environment with a custom domain name. No subdomains are allowed unless you own the top-level domain.

\subsection{CD Pipeline (2.5 pts)}
Code must continually be deployed to production environment using automated GitHub Actions when merged into main.

\subsection{\textcolor{newitem}{NEW:} Vulnerabilities and Linter Findings Fixed (20 pts)}
100\% of vulnerabilities identified by Dependabot and all linter findings from PyLint/Flake8 must be addressed and fixed.

\subsection{\textcolor{newitem}{NEW:} Marketing Video (20 pts)}
Create and upload a 5-minute marketing video to YouTube showcasing your application. Loom offers free screen recording options.

\vspace{2em}
\noindent\textit{See the Common Sprint Requirements document for planning, development, demo, and submission requirements.}

\end{document}
